Clustering of Last.fm Music

### 2015-05-07 writeup/MSDgroupwriteup.tex

The sample data set had  $163206$ songs  $110000$ users, and the number of play counts 
The scale of the data was too large to explore on our computers, so we subset the data down to a size easily handled by an average laptop.

@@

\subsection{Data Analysis}
In order to perform the analysis, we had to fill in a matrix which contained play counts for user and song pairs. We then did a random selection by data element to split between the training (80\%) and testing (20\%) sets.

@@

The bench mark we used to recommend to the top 500 songs to every user.

>>>>

The sample data set had $110000$ users, $163206$ songs, and the number of play counts for each user and song pair.
The scale of the data was too large to explore on our computers, so we subset the data down to a size easily handled by an average laptop.

@@

\subsection{Data Analysis}
In order to perform the analysis, we had to fill in training and testing matrices which contained play counts for user and song pairs. We did a random selection of data elements to split between the training (80\%) and testing (20\%) sets.

@@

The benchmark we used to compare our MAP scores against was recommending the top 500 most popular songs to every user. This naive method resulted in a MAP score of 0.013 (top 500 songs based on counts) or 0.012 (top 500 songs based on plays).
